The Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-11-27 papers/pair-correlation/paper.tex
rewrite last section and conclusion of pair paper Tested on collins. Took 0:47.12.

\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre,aps,10pt]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
  %\includegraphics[width=\columnwidth]{figs/dadz-3-3.pdf}
  %\includegraphics[width=\columnwidth]{figs/dadz-2-2.pdf}
  \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
  %%\includegraphics[width=3cm]{figs/dadz-4-3}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall. For what $\Phi$?}\label{fig:dadz}
\end{figure}

The most relevant quantitative test of a pair distribution function is
how well it predicts the interaction energy due to a pair potential.
To this end, we have computed the error in the first term in a
high-temperature perturbation expansion $a_1$ for several pair
potentials.  In order to focus on effects at the interface, we have
defined a position-dependent pair interaction energy as
\begin{align}
  \frac{dF_1}{dz} &=
  \tfrac12 \int g^{(2)}_{HS}(\rr,\rr')n(\rr)n(\rr')\Phi(|\rr-\rr'|)
  d\rr'\, dxdy
\end{align}
which gives the contribution to the mean-field free energy due to
molecules located at position $z$.  We plot in Figure~\ref{fig:dadz}
this quantity for two pair potentials.

@@

>>>>

\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre,aps,10pt]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{subcaption} % provides subfigure

@@

\begin{figure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-3-2.pdf}
    \vspace{-0.8cm}
    \caption{Sticky hard-sphere fluid}\label{fig:dadz-delta}
  \end{subfigure}
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\columnwidth]{figs/dadz-square-well-3.pdf}
    \vspace{-0.8cm}
    \caption{Hard-core square well fluid}\label{fig:dadz-square-well}
  \end{subfigure}
  \caption{Plot of $\frac{da_1}{dz}$ near a hard
    wall.}\label{fig:dadz}
\end{figure}

A particularly relevant quantitative test of a pair distribution
function is how well it predicts the interaction energy due to a pair
potential.  To this end, we have computed the error in the first term
in a high-temperature perturbation expansion $a_1$ for several pair
potentials.  In order to focus on effects at the interface, we have
defined a position-dependent pair interaction energy as
\begin{align}
  \frac{dF_1}{dz} &=
  \tfrac12 \int g^{(2)}_{HS}(\rr,\rr')n(\rr)n(\rr')\Phi(|\rr-\rr'|)
  d\rr'\, dxdy\label{eq:da1}
\end{align}
which gives the contribution to the mean-field free energy due to
molecules located at position $z$.

We plot in Fig.~\ref{fig:dadz} this quantity for two pair potentials
near a hard wall.  Figure~\ref{fig:dadz-delta} shows the results for a
delta-function interaction at contact, which represents a so-called
``sticky hard-sphere fluid.''  Our pair distribution function is
constructed to produce this result exactly, provided the averaged pair
distribution function at contact from Ref.~\citenum{schulte2012using}
is exact.  As expected, we see excellent agreement with the Monte
Carlo simulation results, while the approximations of Fischer and
Sokolowski each show deviations near the interface.
Figure~\ref{fig:dadz-square-well} shows the same curve from
Eq.~\ref{eq:da1} for a square-well fluid.  We have chosen a square
well fluid with a potential range of 1.79, which is the optimal value
found for a SAFT-based model of water~\cite{clark2006developing}.
This potential stresses our approximation to the radial distribution
function, which results in less satisfactory results near a
hard-sphere diameter from the wall.  We see that over these length
scales, Sokolowski's approximation is very accurate.

@@

We have introduced and tested an approximation for the pair
distribution function of the inhomogeneous hard-sphere fluid.  Our
approximation is suitable for use in the development of classical
density functionals based constructed using perturbation theory, and
may be computed using exclusively single-center convolutions.  We have
tested this function at a hard wall and near a single fixed hard
sphere, and find that it gives qualitatively reasonable results.
Tests of the pair distribution function in integrals that arise in
thermodynamic perturbation theory suggest that our approximation gives
good results for both short-range and long-range attractions.
